---
title: "real data analysis"
author: "Seo Jae Hyun"
date: '2022-11-03'
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(locfit)
library(locpol)
library(rdd)
library(pscl)
library(gridExtra)


```


### Data importing


```{r data importing}


dat = read.csv('S1_Data.csv')

```


### Variable introduction

EarliestCD4Count : Value of Earliest CD4 Count, cells per mm3 contin numeric

QtrOfEarliestCD4Count : Quarter of Earliest CD4 Count (exact date suppressed) discrete character

female : Female discrete numeric

agecat : Age category (exact age suppressed) discrete numeric

Clinic_A : Entered care at Clinic A discrete numeric

Clinic_B : Entered care at Clinic B discrete numeric

Clinic_C : Entered care at Clinic C discrete numeric

Clinic_Other : Entered care at a clinic other than A, B, or C discrete numeric

ART_2w : Started ART within 2 weeks of earliest CD4 count discrete numeric

ART_6m : Started ART within 6 months of earliest CD4 count discrete numeric

ART_12m : Started ART within 12 months of earliest CD4 count discrete numeric

visit_test_6_18 : Retained at 12 months; any labs or clinic visits 6-18 mo after earliest CD4 discrete numeric

test_6_18 : Retained at 12 months; any lab tests 6-18 months after earliest CD4 discrete numeric

test_0_6 : Retained 0-6 months; any lab tests 0-6 months after earliest CD4 discrete numeric

test_6_12 : Retained 6-12 months; any lab tests 6-12 months after earliest CD4 discrete numeric

test_12_18 : Retained 12-18 months; any lab tests 12-18 months after earliest CD4 discrete numeric

test_18_24 : Retained 18-24 months; any lab tests 18-24 months after earliest CD4 discrete numeric

treatment : I(EarliestCD4Count<350)



# basic function


```{r local linear regression}


one_linear_ft_coef_and_var=function(data, value, bw, dire='left'){
  
  if (dire=='left'){
    result=data %>% filter(x<value & x>value-bw)
  }
  else if (dire=='right'){
    result=data %>% filter(x>=value & x<value+bw)
  }
  else {
    result='error : dire must be left or right'
  }
    
  K= dnorm(x=value, mean=result$x, sd=bw)
  data_revision = result %>% mutate(x=x-value)
  est=lm(y~x, data=data_revision)
  
  
  return(list(est$coefficients, vcov(est)))


}


# compute tau_SRD by local linear regression



SRD_lm_coef_var=function(data, value, bw){
  
  
  result_left = one_linear_ft_coef_and_var(data=data, value=value, bw=bw, dire='left')
  result_right = one_linear_ft_coef_and_var(data=data, value=value, bw=bw, dire='right')
  
  
  mu_right = result_right[[1]][1]
  mu_left = result_left[[1]][1]
  
  tauhat=result_right[[1]][1]-result_left[[1]][1]
  
  
  sigma_left=result_left[[2]]
  sigma_right=result_right[[2]]
  
  
  
  nl=sum(data$x<value & data$x>value-bw)
  nr=sum(data$x>value & data$x<value+bw)
  

  asym_var=sigma_left[1, 1]+sigma_right[1, 1]
  
  
  return(c(tauhat, asym_var, mu_left, mu_right))

  
}


newdat = dat %>% select(c(EarliestCD4Count, ART_6m)) %>% mutate(ART_6m = as.numeric(ART_6m))

colnames(newdat) = c('x', 'y')





```




```{r local likelhood}



one_glm_ft_coef_and_var = function(data, value, bw, dire='left', type){
  
  
  if (dire=='left'){
    result=data %>% filter(x<value & x>value-bw)
  }
  else if (dire=='right'){
    result=data %>% filter(x>=value & x<value+bw)
  }
  else {
    result='error : dire must be left or right'
  }
  
  K= dnorm(x=value, mean=result$x, sd=bw)
  data_revision = result %>% mutate(x=x-value)
  est=glm(y~x, data=data_revision, family = type)
  
  
  return(list(est$coefficients, vcov(est)))
  
  
}



# compute tau_SRD by local likelihood



SRD_glm_coef_var = function(data, value, bw, type){
  
  
  result_left = one_glm_ft_coef_and_var(data=data, value=value, bw=bw, dire='left', type)
  result_right = one_glm_ft_coef_and_var(data=data, value=value, bw=bw, dire='right', type)
  
  if (type == 'poisson'){
    
    mu_left = exp(result_left[[1]][1])
    mu_right = exp(result_right[[1]][1])
    
    tau_hat = mu_right - mu_left
    
    sigma_left = result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = mu_left^2*sigma_left[1, 1] + mu_right^2*sigma_right[1, 1]
    
  }
  
  else if (type == 'binomial'){
    
    mu_left = exp(result_left[[1]][1])/(1+exp(result_left[[1]][1]))
    mu_right = exp(result_right[[1]][1])/(1+exp(result_right[[1]][1]))
    tau_hat = mu_right - mu_left
    
    sigma_left =result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = (exp(result_left[[1]][1])/(1+exp(result_left[[1]][1]))^2)^2 * sigma_left[1, 1] + (exp(result_right[[1]][1])/(1+exp(result_right[[1]][1]))^2)^2 * sigma_right[1, 1]
    
  }
  
  else if (type == 'quasipoisson'){
    
    mu_left = exp(result_left[[1]][1])
    mu_right = exp(result_right[[1]][1])
    
    tau_hat = mu_right - mu_left
    
    sigma_left = result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = mu_left^2*sigma_left[1, 1] + mu_right^2*sigma_right[1, 1]
    
  }
  
  
  return(c(tau_hat, asym_var, mu_left, mu_right))

}


newdat$y = ifelse(newdat$y==1, 0, 1)


```




```{r automation}


make_result=function(data, column, cutoff, linbw, locbw){
  
  newdat = data[, c('EarliestCD4Count', column)]
  newdat = newdat %>% filter(newdat[[column]]==1 | newdat[[column]]==0)
  colnames(newdat) = c('x', 'y')
  newdat$y = ifelse(newdat$y==1, 0, 1)
  

  
  lin_result = SRD_lm_coef_var(newdat,cutoff, linbw)
  loc_result = SRD_glm_coef_var(newdat, cutoff, locbw, 'binomial')
  
  result=data.frame('outcome'=c(column, column),'type'=c('loc', 'lin'), 'tau_est' = c(loc_result[1], lin_result[1]), 'tau_var'=c(loc_result[2], lin_result[2]), 'left'=c(loc_result[3], lin_result[3]), 'right'=c(loc_result[4], lin_result[4]))
  
  
  
  
}




```







```{r cv result}



cv_results = read.csv('cv_result.csv')








cv_results = cv_results %>% select(!index)



bandwidth_cv = apply(cv_results, 2, which.max)

bandwidth_cv = bandwidth_cv[c(1, 7, 2, 3, 5, 6, 4)] # sorted by test_name



bandwidth_case = seq(-10, 10, by=0.2)


selector = bandwidth_case[bandwidth_cv]




test_name = c('ART_6m', 'visit_test_6_18', 'test_0_6', 'test_6_12', 'test_12_18', 'test_18_24', 'test_6_18')
bandwidth_lin = c(96.4, 142.1, 114.2, 164.7, 125.4, 164.2, 116.8) # results from paper



bw_loc = bandwidth_lin + selector



```



```{r after selection}

test_name = c('ART_6m', 'test_0_6', 'test_6_12', 'test_6_18', 'test_12_18', 'test_18_24', 'visit_test_6_18')

result = make_result(data=dat, column='ART_6m', cutoff=350, linbw=96.4, locbw=86.4)

for (i in 2:7){
  
  result = rbind(result, make_result(data=dat, column=test_name[i], cutoff=350, linbw=bandwidth_lin[i], locbw=bw_loc[i]))
  
}

result = result %>% mutate(tau_est = round(tau_est, 5),
                          tau_var = round(tau_var, 6),
                          left = round(left, 3),
                          right = round(right, 3))

result = result %>% mutate(ci_left = tau_est - round(qnorm(0.975, 0, 1)*sqrt(tau_var), 3),
                           ci_right = tau_est + round(qnorm(0.975, 0, 1)*sqrt(tau_var), 3),
                           p_val = 1-qnorm(tau_est/sqrt(tau_var), 0, 1))

p_val =c()

for (i in 1: dim(result)[1]){
  
  p_val = c(p_val, round((1-(pnorm(result$tau_est[i]/sqrt(result$tau_var[i]), 0, 1)))*2, 3))
  
}



result$p_val = p_val




final = result %>% mutate(ci_left=(round(ci_left*100, 1)),
                  ci_right=(round(ci_right*100, 1)),
                  tau_est = abs(round(tau_est*100, 1))) %>% filter(type=='loc')

write.csv(final, 'real data analysis result.csv')

```







