---
title: "real data analysis"
author: "Seo Jae Hyun"
date: '2022-11-03'
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(locfit)
library(locpol)
library(rdd)
library(pscl)
library(gridExtra)


```


### Data importing


```{r data importing}


dat = read.csv('S1_Data.csv')

```


### Variable 소개

EarliestCD4Count : Value of Earliest CD4 Count, cells per mm3 contin numeric

QtrOfEarliestCD4Count : Quarter of Earliest CD4 Count (exact date suppressed) discrete character

female : Female discrete numeric

agecat : Age category (exact age suppressed) discrete numeric

Clinic_A : Entered care at Clinic A discrete numeric

Clinic_B : Entered care at Clinic B discrete numeric

Clinic_C : Entered care at Clinic C discrete numeric

Clinic_Other : Entered care at a clinic other than A, B, or C discrete numeric

ART_2w : Started ART within 2 weeks of earliest CD4 count discrete numeric

ART_6m : Started ART within 6 months of earliest CD4 count discrete numeric

ART_12m : Started ART within 12 months of earliest CD4 count discrete numeric

visit_test_6_18 : Retained at 12 months; any labs or clinic visits 6-18 mo after earliest CD4 discrete numeric

test_6_18 : Retained at 12 months; any lab tests 6-18 months after earliest CD4 discrete numeric

test_0_6 : Retained 0-6 months; any lab tests 0-6 months after earliest CD4 discrete numeric

test_6_12 : Retained 6-12 months; any lab tests 6-12 months after earliest CD4 discrete numeric

test_12_18 : Retained 12-18 months; any lab tests 12-18 months after earliest CD4 discrete numeric

test_18_24 : Retained 18-24 months; any lab tests 18-24 months after earliest CD4 discrete numeric

treatment : I(EarliestCD4Count<350)




```{r eda}




for (i in 2:17){
  
  dat[, i] = factor(dat[, i])
  
}


dat = dat %>% mutate(treatment = EarliestCD4Count<350)




```



```{r local linear regression}


one_linear_ft_coef_and_var=function(data, value, bw, dire='left'){
  
  if (dire=='left'){
    result=data %>% filter(x<value & x>value-bw)
  }
  else if (dire=='right'){
    result=data %>% filter(x>=value & x<value+bw)
  }
  else {
    result='error : dire must be left or right'
  }
    
  K= dnorm(x=value, mean=result$x, sd=bw)
  data_revision = result %>% mutate(x=x-value)
  est=lm(y~x, data=data_revision)
  
  
  return(list(est$coefficients, vcov(est)))


}


# compute tau_SRD by local linear regression



SRD_lm_coef_var=function(data, value, bw){
  
  
  result_left = one_linear_ft_coef_and_var(data=data, value=value, bw=bw, dire='left')
  result_right = one_linear_ft_coef_and_var(data=data, value=value, bw=bw, dire='right')
  
  
  mu_right = result_right[[1]][1]
  mu_left = result_left[[1]][1]
  
  tauhat=result_right[[1]][1]-result_left[[1]][1]
  
  
  sigma_left=result_left[[2]]
  sigma_right=result_right[[2]]
  
  
  
  nl=sum(data$x<value & data$x>value-bw)
  nr=sum(data$x>value & data$x<value+bw)
  

  asym_var=sigma_left[1, 1]+sigma_right[1, 1]
  
  
  return(c(tauhat, asym_var, mu_left, mu_right))

  
}


newdat = dat %>% select(c(EarliestCD4Count, ART_6m)) %>% mutate(ART_6m = as.numeric(ART_6m))

colnames(newdat) = c('x', 'y')





```




```{r local likelhood}



one_glm_ft_coef_and_var = function(data, value, bw, dire='left', type){
  
  
  if (dire=='left'){
    result=data %>% filter(x<value & x>value-bw)
  }
  else if (dire=='right'){
    result=data %>% filter(x>=value & x<value+bw)
  }
  else {
    result='error : dire must be left or right'
  }
  
  K= dnorm(x=value, mean=result$x, sd=bw)
  data_revision = result %>% mutate(x=x-value)
  est=glm(y~x, data=data_revision, family = type)
  
  
  return(list(est$coefficients, vcov(est)))
  
  
}



# compute tau_SRD by local likelihood



SRD_glm_coef_var = function(data, value, bw, type){
  
  
  result_left = one_glm_ft_coef_and_var(data=data, value=value, bw=bw, dire='left', type)
  result_right = one_glm_ft_coef_and_var(data=data, value=value, bw=bw, dire='right', type)
  
  if (type == 'poisson'){
    
    mu_left = exp(result_left[[1]][1])
    mu_right = exp(result_right[[1]][1])
    
    tau_hat = mu_right - mu_left
    
    sigma_left = result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = mu_left^2*sigma_left[1, 1] + mu_right^2*sigma_right[1, 1]
    
  }
  
  else if (type == 'binomial'){
    
    mu_left = exp(result_left[[1]][1])/(1+exp(result_left[[1]][1]))
    mu_right = exp(result_right[[1]][1])/(1+exp(result_right[[1]][1]))
    tau_hat = mu_right - mu_left
    
    sigma_left =result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = (exp(result_left[[1]][1])/(1+exp(result_left[[1]][1]))^2)^2 * sigma_left[1, 1] + (exp(result_right[[1]][1])/(1+exp(result_right[[1]][1]))^2)^2 * sigma_right[1, 1]
    
  }
  
  else if (type == 'quasipoisson'){
    
    mu_left = exp(result_left[[1]][1])
    mu_right = exp(result_right[[1]][1])
    
    tau_hat = mu_right - mu_left
    
    sigma_left = result_left[[2]]
    sigma_right = result_right[[2]]
    
    asym_var = mu_left^2*sigma_left[1, 1] + mu_right^2*sigma_right[1, 1]
    
  }
  
  
  return(c(tau_hat, asym_var, mu_left, mu_right))

}


newdat$y = ifelse(newdat$y==1, 0, 1)


```




```{r automation}


make_result=function(data, column, cutoff, linbw, locbw){
  
  newdat = data[, c('EarliestCD4Count', column)]
  newdat = newdat %>% filter(newdat[[column]]==1 | newdat[[column]]==0)
  colnames(newdat) = c('x', 'y')
  newdat$y = ifelse(newdat$y==1, 0, 1)
  

  
  lin_result = SRD_lm_coef_var(newdat,cutoff, linbw)
  loc_result = SRD_glm_coef_var(newdat, cutoff, locbw, 'binomial')
  
  result=data.frame('outcome'=c(column, column),'type'=c('loc', 'lin'), 'tau_est' = c(loc_result[1], lin_result[1]), 'tau_var'=c(loc_result[2], lin_result[2]), 'left'=c(loc_result[3], lin_result[3]), 'right'=c(loc_result[4], lin_result[4]))
  
  
  
  
}


result = make_result(data=dat, column='ART_6m', cutoff=350, linbw=96.3, locbw=100)

colname = colnames(dat)

for (i in 12:17){
  
  result = rbind(result, make_result(data=dat, column=colname[i], cutoff=350, linbw=100, locbw=100))
  
}

result = result %>% mutate(tau_est = round(tau_est, 5),
                          tau_var = round(tau_var, 6),
                          left = round(left, 3),
                          right = round(right, 3))





```




```{r cv}


### Cross-validation


### Finding quantile

quntilerange=function(data, q,cutoff){
  
  return(c(quantile(data$x[data$x<cutoff], q), quantile(data$x[data$x>=cutoff], 1-q)))
}




### Cross-validation

cv_rd_srd = function(newdata, column, cutoff, q, bw, type='binomial'){
  
  
  newdat = newdata[, c('EarliestCD4Count', column)]
  newdat = newdat %>% filter(newdat[[column]]==1 | newdat[[column]]==0)
  colnames(newdat) = c('x', 'y')
  newdat$y = ifelse(newdat$y==1, 0, 1)
  data = newdat
  cvrange=quntilerange(data=data, q=q, cutoff=cutoff)
  
  
  check_df=data[data$x>=cvrange[1] & data$x<=cvrange[2], ]
  check_x=check_df$x
  
  
  result=NULL
  
  
  if (type=='ZIP'){
    
    for (i in 1:length(check_x)){
      if (check_x[i]<cutoff){
        re = one_zeroinfl_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='left')[[1]]
      }
      else if (check_x[i]>=cutoff){
        
        re = one_zeroinfl_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='right')[[1]]
      }
      
      pi=exp(re$zero[1])/(1+exp(re$zero[1]))
      lambda=exp(re$count[1])
      
      check_y = check_df[i, 'y']
      
      like = ifelse(check_y==0, log(pi +(1-pi)*exp(-lambda)), log(1-pi) - lambda + check_y*log(lambda))
      
      result=c(result, like)
      
    }
  }
  
  
  else if (type=='linear'){
    
    for (i in 1:length(check_x)){
      
      if (check_x[i]<cutoff){
        
        re=one_linear_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='left')[[1]]
      }
      else if (check_x[i]>=cutoff){
        
        
        re=one_linear_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='right')[[1]]
      }
      
      mu=re[1]
      result=c(result, mu)
    }
    
    return(mean((check_df$y-result)^2))
  }
  
  
  else {
    
    for (i in 1:length(check_x)){
      if (check_x[i]<cutoff){
        re = one_glm_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='left', type=type)[[1]]
        
      }
      else{
        
        re = one_glm_ft_coef_and_var(data=data, value=check_x[i], bw=bw, dire='right', type=type)[[1]]
        
      }
      
      check_y = check_df[i, 'y']
      
      if (type =='binomial'){
        
        pi = exp(re[1])/(1+exp(re[1]))
        like = check_y * log(pi/(1-pi)) + log(1-pi)
        
      }
      else{
        
         lambda = exp(re[1])
        like = -lambda + y*log(lambda)
      }
      
      result = c(result, like)
    }
    
    
  }
  
  return(sum(result))
  
}





```



y : ART_6m, visit_test_6_18, test_0_6, test_6_12, test_12_18, test_18_24, test_6_18

bw : 96.4, 142.1, 114.2, 164.7, 125.4, 164.2, 116.8


```{r cv bandwidth setting}




test_name = c('ART_6m', 'visit_test_6_18', 'test_0_6', 'test_6_12', 'test_12_18', 'test_18_24', 'test_6_18')
bandwidth_lin = c(96.4, 142.1, 114.2, 164.7, 125.4, 164.2, 116.8)


colname


check_bw = function(newdata, column, cutoff, q, bw_center){
  
  
  results = c()
  
  
  bw = bw_center + seq(-10, 10, by=0.2)
  
  
  for (i in 1:length(bw)){
    
    
    result = cv_rd_srd(newdata=newdata, column = column, cutoff=cutoff, q=q, bw=bw[i])
    
    results = c(results, result)
    
    print(paste0(i, ' working'))
    
  }

  
  return(results)
  
}



result = check_bw(dat, test_name[2], 350, 0.5, bandwidth_lin[2])

write.csv(result, 'visit_test_6_18.csv')



```


